---
output:
  html_document: default
  pdf_document: default
---
We will look at technique to find relation and correlation between 2 variables. 
The correlation coefficient is only able to tell if there exists a linear relationship,
so we need to visualize the data so we don't miss non-linear relationships 
Copying the DataFrame in to a conveniently named one
library(SDSFoundations)
```{r}
library(SDSFoundations)
bulls <- BullRiders
```
Creating a scatterplot between variables we wish to examine
```{r}
plot(bulls$YearsPro,bulls$BuckOuts14, ylab='Buckouts',xlab = 'Years Pro', main= 'Years Vs Buckouts')
```
The dots are all over the place and the relation is not looking linear, let us confirm by tracing a line
```{r}
plot(bulls$YearsPro,bulls$BuckOuts14, ylab='Buckouts',xlab = 'Years Pro', main= 'Years Vs Buckouts')+
abline(lm(bulls$YearsPro~bulls$BuckOuts14))
```
We confirm that linear relationship doesn't exist, we expect the correlation coefficient to be poor.
```{r}
cor(bulls$YearsPro,bulls$BuckOuts14)
```
Let us try the same with Events held in 2014 and the respective Buckouts

```{r}
plot(bulls$Events14,bulls$BuckOuts14, ylab='Buckouts',xlab = 'Events', main= 'Events Vs Buckouts')
```
Very strong relationship can be observed in scatterplot, let us confirm by calculation corr. coeff.
```{r}
plot(bulls$Events14,bulls$BuckOuts14, ylab='Buckouts',xlab = 'Events', main= 'Events Vs Buckouts')+abline(lm(bulls$BuckOuts14~bulls$Events14))
```
```{r}
cor(bulls$Events14,bulls$BuckOuts14)
```
Build a nice little table for quick correlation infor between variables. Storing the variables of interest in a vector
```{r}
corvar <- c('YearsPro','Events14','BuckOuts14')
```
Calculating correlatin between them, rounded to 2 digits
```{r}
round(cor(bulls[,corvar]),2)
```

*This analysis can say that there is a strong linear relation between the participation of a rider at event and the number of BuckOuts*
